Price of Anarchy for Mean Field Games

### 2018-07-03 PoA.tex
major point 7

\subsection{\textbf{Numerical Results}}

Using the explicit formulas derived in Appendix \ref{appendix_solving_fbsdes}, we numerically compute the price of anarchy when the coefficients are time-independent, nonnegative, and satisfy assumption (\ref{eq:assumptions}). In particular, when we allow for full interaction (i.e. through the states and the controls), we choose the following default values:

>>>>

\subsection{\textbf{Numerical Results}}
The solutions to the problems we have considered are given by the formulas derived in Appendix \ref{appendix_solving_fbsdes}, which are explicit up to evaluating integrals. Using the simple rectangle rule to evaluate integrals, we numerically compute the price of anarchy when the coefficients are time-independent, nonnegative, and satisfy assumption (\ref{eq:assumptions}). In particular, when we allow for full interaction (i.e. through the states and the controls), we choose the following default values:
